\chapter{Recommendations}
This section is aimed at sharing our experiences and recommendations for the future. General aspects about quadcopters, project management, teamwork, planning, the design and implementation of the quadcopters are some of the subjects mentioned. \\

During the planning phase, several things can help the structure and effectiveness of the project. Knowing the project model can be of great help if used correctly. Spend time as early as possible in the project to learn the project model, and to make sure that everyone in the group understands it. Milestones and intermediate objectives must be stated in clear text to avoid confusion.\bigskip 

A documentation and code standard should be agreed upon as early as possible, and can help to reduce time usage and need for reviews. Make sure to back-up all documentation and text while ensuring traceability. During the project there are multiple things to watch out for, such as development loops. Efficiency is important, make sure to use all the resources available, this includes people, cost and equipment. Be careful not to misuse each others time, be sure to review and update the project plan often, it is probably not perfect the first time around. Another tip is to continuously work on the documentation for the project, do not save it for later. \bigskip

Consult people with knowledge, but be critical to their advice. The people in the team are the ones best suited to determine if the advise of substance and discuss in plural. Communication and teamwork is imperative for the project to succeed. Misunderstandings are common and unavoidable, especially with interdisciplinary teams.\bigskip 

Be sure to understand your undertakings and how long time things may take. Creating and building in the physical world is time consuming and many things will probably go wrong. When ordering parts, be skeptical of the what you order. There exists a lot of poor quality components, make sure to buy high quality components the first time around from reliable vendors. Ensure absolute mechanical precision if you are going to work with a variable pitch quadcopter. Ensure enough spare parts, things will break.\\

Summed up:
\begin{itemize}
    \item Get to know the project model
    \item Set clear and understandable milestones and intermediate objectives. 
    \item Agree on documentation and code standard as early as possible
    \item Watch out for development loops
    \item Use all resources available
    \item Take advise from people who knows the field, but be critical
    \item Communication and teamwork is imperative. Remember to communicate.
    \item Be skeptical of parts you order online
    \item Making a flight controller is time consuming
    \item Use a more powerful microcontroller
    \item Consider creating a optimized PCB. 
\end{itemize}



